Maps and spatial stats demo

### 2025-04-24 recaptureanalysis/Mapdemo.qmd
Prepping for EDI update.

#The WW_Delta dataset is a spatial polygon datset
View(deltamapr::WW_Delta)
#The geometry column starts with "Polygon" and then has latitudes and longitudes
```

@@

>>>>

#The WW_Delta dataset is a spatial polygon datset
View(deltamapr::WW_Delta)
#The geometry column starts with "Polygon" and then has latitudes and longitudes

st_write(deltamapr::P_Stations, dsn = "recaptureanalysis/GISfiles/P_stations.shp")
st_write(deltamapr::WW_Delta, dsn = "recaptureanalysis/GISfiles/WW_Delta.shp")

@@

newww = st_read("recaptureanalysis/GISfiles/WW_Delta.shp")
